---
title: 'Association Rules: Medical Appoinyments'
output:
  html_document:
    df_print: paged
---

```{r}
library("arules")
library("arulesViz")
```

#Read the dataset in csv format


```{r}
noshow<-read.table("noshow.csv",dec=".",sep=",",header=TRUE,colClasses=c("numeric","factor","factor","factor","factor","factor","factor","factor","factor","factor","factor","factor","numeric"))
ds<-noshow
```

#Convert numeric fields into categorical ones
```{r}
ds[["Age"]] <- ordered(cut(ds[["Age"]], c(-5,10,18,30,50,70,105)),
labels = c("Child", "Young", "Adult", "Middle-Aged", "Senior", "Old"))

ds[["AwaitingTime"]] <- ordered(cut(ds[["AwaitingTime"]], c(-400,-180,-90,-30,-7,-1)),
labels = c(">6months", "[3,6]months", "[1,3]months", "[1,3]weeks", "1week"))
```


#Convert the dataset from data.frame format into transactions format
```{r}
ds.trans <- as(ds,"transactions")
ds.trans@itemInfo$labels
```



#Lunch the Apriori Algorithm
```{r}
rules <- apriori(ds.trans,parameter=list(minlen=2, maxlen=4, support=0.001,confidence=0.4),control = list(verbose=F))
```


#Remove redundant rules
```{r}
rules <- (rules[!is.redundant(rules)])
```


#Extract subsets of rules of interest
```{r}
noshow <- subset(rules,(rhs %in% paste0("Status=No-Show")))
showup <- subset(rules,(rhs %in% paste0("Status=Show-Up")))
```


#Inspect the best 10 rules according to the lift and try to provide a miningful explanation
```{r}
noshow.sorted <- sort(noshow, by="lift")
inspect(noshow.sorted[1:10])
plot(noshow.sorted[1:10],method="graph",control=list(main = "Top 10 rules for 'No-Show'"))
```

```{r}
showup.sorted <- sort(showup, by="lift")
inspect(showup.sorted[1:10])
plot(showup.sorted[1:10],method="graph",control=list(main = "Top 10 rules for 'Show-Up'"))
```



#Further investigate the best noshow-rules

```{r}
inspect(noshow.sorted[1:1])
plot(noshow.sorted[1:1],method="doubledecker",data = ds.trans, control=list(main = "Double-Decker Plot"))

```

```{r}
inspect(showup.sorted[1:1])
plot(showup.sorted[1:1],method="doubledecker",data = ds.trans, control=list(main = "Double-Decker Plot"))
```


```{r}
rules.sorted <- sort(rules, by="lift")
inspect(rules.sorted[1:1])
plot(rules.sorted[1:1],method="doubledecker",data = ds.trans, control=list(main = "Double-Decker Plot"))

```

